Target Markdown

### 2023-04-14 _targets.Rmd
...

      tar_target(matching, match(db_path, ids, gender)),
      tar_target(sup_path, here::here("data", "raw", "supervisors_control.csv"), format = "file"),
      tar_target(sup_control, read.csv2(sup_path)),

@@

    tar_target(full_indicator,
               calc_full_indicator(independent_topics),

>>>>

      tar_target(matching, match(db_path, ids, gender)),
      tar_target(sup_path, here::here("data", "raw", "supervisors_control_final.csv"), format = "file"),
      tar_target(sup_control, read.csv2(sup_path)),

@@

    tar_target(full_indicator,
               calc_full_indicator(independent_topics))
